final_project_draft

### 2022-04-25 draft.Rmd
April 25th graded before class commit. Found a new data set and worked on style component of project.

ggplot(data = high_donations, aes(x = amount, y = owner_ordered, label = Recipient, colour = party)) +
  geom_point(size = 2) +
  labs(x = " ", 
       y = " ",
       title = "How Much Did NFL Owners Donate in 2016?",
       colour = "Political Party",
       subtitle = "What Influence Could NFL Team Owners Have on Elections?") +
  scale_colour_viridis_d() +
  theme_bw() +
  theme(plot.title = element_text(family = "mono",
                                  face = "bold",
                                  size = 15,
                                  margin = margin(c(t = 20,
                                                    b = 50,
                                                    vjust = 10))),
        plot.subtitle = element_text(family = "mono",
                                     face = "italic",
                                     size = 10),
        legend.title = element_text(family = "mono",
                                    face = "bold",
                                    size = 8),
        legend.text = element_text(family = "mono",
                                   size = 8),
        axis.text = element_text(family = "mono",
                                 size = 8),
        legend.box.background = element_rect(),
        legend.position = "bottom") 
```

@@

ggplot(data = frequent, aes(x = amount, y = level_order, label = Amount, colour = Party)) +
  geom_point() +
  labs(title = "How Many Donations Have They Made?",
       subtitle = "Examining The Monetary Amount of Observed Political Donations",
       y = " ",
       x = " ",
       colour = "Party") +
  scale_colour_brewer(palette = "Dark2") +
    theme_bw() +
  theme(legend.position = "bottom",
        plot.title = element_text(family = "mono",
                                  face = "bold",
                                  size = 12),
        axis.text.x = element_text(family = "mono"),
        axis.text.y = element_text(family = "mono"),
        legend.title = element_text(family = "mono", 
                                    face = "bold",
                                    size = 5),
        legend.text = element_text(family = "mono",
                                   size = 5),
        plot.subtitle = element_text(family = "mono",
                                     face = "italic",
                                     size = 9),
        legend.box.background = element_rect())
```

## Only average - no political party 
``` {r}
ggplot(data = frequent, aes(x = amount, y = level_order, label = Amount, colour = Party)) +
  geom_point() +
  geom_point(data = average_donation, aes(x = mean, colour = "Mean Donations")) +
  labs(title = "How Many Donations Have They Made?",
       subtitle = "Examining The Monetary Amount of Observed Political Donations",
       y = " ",
       x = " ",
       colour = "Party") +
  scale_colour_brewer(palette = "Dark2") +
  scale_colour_manual(values = c("Mean Donations" = "red")) +
    theme_bw() +
  theme(legend.position = "bottom",
        plot.title = element_text(family = "mono",
                                  face = "bold",
                                  size = 12,
                                  margin = margin(c(t = 50,
                                                    b = 50)),
                                  vjust = 10),
        axis.text.x = element_text(family = "mono"),
        axis.text.y = element_text(family = "mono"),
        legend.title = element_text(family = "mono", 
                                    face = "bold",
                                    size = 7),
        legend.text = element_text(family = "mono",
                                   size = 6),
        plot.subtitle = element_text(family = "mono",
                                     face = "italic",
                                     size = 9,
                                     vjust = 5),
        legend.box.just = "left",
        legend.box.background = element_rect())
```

## With average but no way to distinguish
```{r}
ggplot(data = frequent, aes(x = amount, y = level_order, label = Amount, colour = Party)) +
  geom_point() +
  geom_point(data = average_donation, aes(x = mean, colour = "Mean Donations"))+
  labs(title = "How Many Donations Have They Made?",
       subtitle = "Examining The Monetary Amount of Observed Political Donations",
       y = " ",
       x = " ",
       colour = "Party") +
  scale_colour_viridis_d() +
    theme_bw() +
  theme(legend.position = "bottom",
        plot.title = element_text(family = "mono",
                                  face = "bold",
                                  size = 12,
                                  margin = margin(c(t = 50,
                                                    b = 50)),
                                  vjust = 10),
        axis.text.x = element_text(family = "mono"),
        axis.text.y = element_text(family = "mono"),
        legend.title = element_text(family = "mono", 
                                    face = "bold",
                                    size = 7),
        legend.text = element_text(family = "mono",
                                   size = 6),
        plot.subtitle = element_text(family = "mono",
                                     face = "italic",
                                     size = 9,
                                     vjust = 5),
        legend.box.just = "left",
        legend.box.background = element_rect())

  scale_fill_discrete(limits = c("Republican", "Democrat", 
                                      "Bipartisan, but mostly Republican", 
                                      "Bipartisan", "N/A",
                                      "Bipartisan, but mostly Democratic",
                                      "Independent", 
                                      "Mean Donations"))

frequent %>% mutate(party = fct_relevel(Party, c("Republican", "Democrat", 
                                      "Bipartisan, but mostly Republican", 
                                      "Bipartisan", "N/A",
                                      "Bipartisan, but mostly Democratic",
                                      "Independent", 
                                      "Mean Donations")))
```

## sum of all donations
```{r}
sum_donations <- frequent %>% group_by(Owner) %>%
  summarise(sum = sum(amount)) %>%
  rename(Sum = 'sum') %>%
  arrange(desc(Sum))
sum_donations

@@

ggplot(data = cj_party, aes(x = party, y = n, fill = Party)) +
  geom_col() +
  coord_flip() +
  scale_fill_brewer(palette= "Pastel2") +
  labs(title = "Party Affiliation of Political Donations Made by Charles Johnson",
       x = " ",
       y = " ") +
  theme(legend.position = "bottom",
        plot.title = element_text(family = "mono",
                                  face = "bold",
                                  hjust = 0.5,
                                  size = 13,
                                  margin = margin(c(t = 50,
                                                    b = 50)),
                                  vjust = 10),
        axis.text = element_text(family = "mono"),
        legend.title = element_text(family = "mono",
                                    face = "bold"),
        legend.text = element_text(family = "mono"),
        axis.ticks.y = element_blank(),
        axis.ticks.x = element_blank(),
        axis.title.x = element_text(family = "mono",
                                    size = 9,
                                    face = "italic",
                                    margin = margin(t = 20)),
        axis.title.y = element_text(family = "mono",
                                    margin = margin(t = 20, b = 20, r = 20)))

@@

ggplot(data = recipients, aes(x = recipient, y = n, fill = Party)) +
  geom_col() +
  coord_flip() +
  labs(x = " ",
       y = "Count of Donations") +
  labs(title = "Organizations Receiving Most Donations Among All Owners") +
  scale_fill_brewer(palette = "Accent") +
  theme(legend.position = "bottom") +
  scale_x_discrete(labels = new_names) +
  theme(plot.title = element_text(family = "mono",
                                  face = "bold",
                                  margin = margin(c(t = 50,
                                                    b = 50)),
                                  vjust = 7),
        axis.text = element_text(family = "mono"),
        axis.title = element_text(family = "mono",
                                  size = 8),
        axis.title.x = element_text(size = 10,
                                    margin = margin(t = 10,
                                                    b = 10)),
        legend.title = element_text(family = "mono",
                                    face = "bold"),
        legend.text = element_text(family = "mono"),
        axis.ticks = element_blank(),
         legend.box.background = element_rect())

@@

ggplot(data = top10, aes(x = order, y = NetWorth, fill = Industry)) +
  geom_col() +
  coord_flip() +
  labs(x = "Billionaire", 
       y = "Net Worth",
       caption = "Measured in Billions",
       colour = "Industry",
       title = "2021 Forbes Billionaires with the Highest Net Worth") +
  scale_fill_viridis_d() +
  scale_x_discrete(labels = new_names2) +
  theme(legend.position = "bottom") +
  theme(axis.title = element_text(family = "mono",
                                  face = "bold",
                                  margin = margin(c(t = 30,
                                                    b = 30))),
        legend.box.spacing = unit(0.5, 'cm'),
        axis.text = element_text(family = "mono"),
        axis.ticks = element_blank(),
        plot.title = element_text(family = "mono",
                                  face = "bold",
                                  margin = margin(c(t = 15,
                                                    b = 15,
                                                    vjust = 15))),
        legend.margin = margin(c(t = 30)),
        legend.title = element_text(family = "mono",
                                    face = "bold"),
        legend.text = element_text(family = "mono",
                                   face = "italic"),
        plot.caption = element_text(family = "mono",
                                    face = "italic",
                                    vjust = 45,
                                    hjust = 0.5,
                                    margin = margin(c(t = 30,
                                                      b = 30))),
        legend.key.size = unit(.3, 'cm'))
```

@@

check <- countries_10 %>% filter(age < 25 | age > 97)
check

filter <- countries_10 %>% filter(!is.na(age))
filter
filter2 <- filter %>% group_by(Country) %>%
  summarise(Average = mean(age)) %>%
  mutate(order = fct_reorder(.f = Country, .x = Average))
filter3 <- filter2 %>% rename(age = 'Average')
```

## Outliers labeled 
```{r}
ggplot(data = countries_10, aes(x = Country, y = age)) +
  geom_point(alpha = 0.4) +
  coord_flip() +
  geom_point(data = filter2, aes(x = order, y = Average, colour = "Mean Age of Billionaires"),
             size = 2.5) +
  scale_colour_manual(values = c("Mean Age of Billionaires" = "red")) +
  labs(x = "Country", 
       y = "Age",
       title = "Average Age of Billionaires by Country") +
  theme(legend.position = "bottom") +
  theme(axis.title = element_text(family = "mono",
                                  face = "bold"),
        axis.text = element_text(family = "mono"),
        plot.title = element_text(family = "mono",
                                  face = "bold"),
        axis.ticks = element_blank(),
        legend.title = element_blank(),
        legend.text = element_text(family = "mono",
                                   face = "italic"), 
        plot.caption = element_text(family = "mono",
                                    size = 9,
                                    face = "italic")) 
```

@@

ggplot(data = above_or_below_us, aes(x = order, y = networth, colour = above_avg)) +
  geom_segment(aes(x = order, xend = order, y = avg, yend = networth)) +
  geom_point() +
  coord_flip() +
  labs(x = "Name",
      y = "Net Worth",
      caption = "Measured in Billions",
      colour = "Average",
      title = "Billionaires In The Fashion Industry",
      subtitle = "Do these billionaires fall above or below the average billionaire net worth in the U.S.?") +
  theme(axis.text = element_text(family = "mono"),
        axis.title = element_text(family = "mono"),
        legend.text = element_text(family = "mono"),
        legend.title = element_text(family = "mono"),
        plot.caption = element_text(family = "mono",
                                    hjust = 0.5),
        plot.title = element_text(family = "mono"),
        plot.subtitle = element_text(family = "mono"),
        axis.ticks = element_blank())
```

@@

ggplot(data = country_30, aes(x = order, y = n)) +
  geom_point(colour = "orange") +
  geom_segment(aes(x = order, xend = order, y = 0, yend = n), colour = "blue", linetype = "dotdash") +
  coord_flip() +
  theme_light() +
  theme(axis.ticks.x = element_blank()) +
  labs(x = "Country", 
       y = "Count of Billionaires",
       title = "How Many Billionaires Are There From the Top 30 Countries?") +
  theme(plot.title = element_text(family = "mono"),
        axis.text = element_text(family = "mono"),
        axis.title = element_text(family = "mono"))
```

## Playing Around with New Variables - looking at self made billionaires, education level of billionaires 
```{r}
self_made <- forbes_billionaires %>% group_by(Self_made) %>%
  summarise(n = n())

ggplot(data = forbes_billionaires, aes(x = Self_made)) +
  geom_bar()

industry <- billionaires %>% group_by(Industry) %>%
  summarise(n = n()) %>%
  arrange(desc(n))
industry

combined_billionaires <- left_join(forbes_billionaires, billionaires, by = c("Name" = "Name"))
combined_billionaires

@@

harvard <- tidy_education %>% filter(University == "Harvard University")
harvard

@@

ggplot(data = tidy_education2, aes(x = Degree, y = NetWorth)) +
  geom_violin() +
  coord_flip()

library(ggridges)
ggplot(data = tidy_education2, aes(x = Degree, y = NetWorth)) +
  geom_density_ridges()
```

## Forbes Billionaire 2021 3.0 Data Set 
```{r}
forbes_billionaires_geo <- read_csv("data/forbes_billionaires_geo.csv")
forbes_billionaires_geo 
```

>>>>

ggplot(data = high_donations, aes(x = amount, y = owner_ordered, label = Recipient, colour = party)) +
  geom_point(size = 3) +
  labs(x = " ", 
       y = " ",
       title = "How Much Did NFL Owners Donate in 2016?",
       colour = "Political Party",
       subtitle = "What Influence Could NFL Team Owners Have on Elections?") +
  scale_colour_viridis_d() +
  theme_bw() +
  theme(plot.title = element_text(family = "mono",
                                  face = "bold",
                                  size = 18,
                                  margin = margin(c(t = 20,
                                                    b = 50,
                                                    vjust = 15))),
        plot.subtitle = element_text(family = "mono",
                                     face = "italic",
                                     size = 15,
                                     vjust = 2.5),
        legend.title = element_text(family = "mono",
                                    face = "bold",
                                    size = 8),
        legend.text = element_text(family = "mono",
                                   size = 8),
        axis.text = element_text(family = "mono",
                                 size = 8),
        axis.text.x = element_text(face = "bold"),
        axis.text.y = element_text(face = "bold"),
        legend.box.background = element_rect(),
        axis.ticks = element_blank(),
        legend.key.size = unit(1.3, 'cm'),
        legend.position = "bottom") 
```

@@

ggplot(data = frequent, aes(x = amount, y = level_order, label = Amount, colour = Party)) +
  geom_point() +
  labs(title = "How Many Donations Have They Made?",
       subtitle = "Examining The Monetary Amount of Observed Political Donations",
       y = " ",
       x = " ",
       colour = "Party") +
  scale_colour_brewer(palette = "Dark2") +
    theme_bw() +
  theme(legend.position = "bottom",
        plot.title = element_text(family = "mono",
                                  face = "bold",
                                  size = 18,
                                   margin = margin(c(t = 20,
                                                    b = 50,
                                                    vjust = 15))),
        axis.text.x = element_text(family = "mono",
                                   face = "bold"),
        axis.text.y = element_text(family = "mono",
                                   face = "bold"),
        legend.title = element_text(family = "mono", 
                                    face = "bold",
                                    size = 10),
        legend.text = element_text(family = "mono",
                                   size = 8),
        plot.subtitle = element_text(family = "mono",
                                     face = "italic",
                                     size = 15,
                                     vjust = 2.5),
        axis.ticks = element_blank(),
        legend.key.size = unit(0.8, 'cm'),
        legend.box.background = element_rect())
```

## Question: What is the sum of all of the donations made by these owners? 
```{r}
sum_donations <- frequent %>% group_by(Owner) %>%
  summarise(sum = sum(amount)) %>%
  rename(Sum = 'sum') %>%
  arrange(desc(Sum))
sum_donations

@@

ggplot(data = cj_party, aes(x = party, y = n, fill = Party)) +
  geom_col(colour = "black") +
  coord_flip() +
  scale_fill_brewer(palette= "Pastel2") +
  labs(title = "Party Affiliation of Political Donations Made by Charles Johnson",
       x = " ",
       y = " ") +
  theme(legend.position = "bottom",
        plot.title = element_text(family = "mono",
                                  face = "bold",
                                  hjust = 0.5,
                                  size = 18,
                                  margin = margin(c(t = 50,
                                                    b = 50)),
                                  vjust = 10),
        axis.text = element_text(family = "mono",
                                 face = "bold"),
        legend.title = element_text(family = "mono",
                                    face = "bold"),
        legend.text = element_text(family = "mono"),
        axis.ticks.y = element_blank(),
        axis.ticks.x = element_blank(),
        axis.title.x = element_text(family = "mono",
                                    size = 9,
                                    face = "italic",
                                    margin = margin(t = 20)),
        axis.title.y = element_text(family = "mono",
                                    margin = margin(t = 20, b = 20, r = 20)),
        legend.key.size = unit(0.8, 'cm'),
        legend.box.background = element_rect())

@@

ggplot(data = recipients, aes(x = recipient, y = n, fill = Party)) +
  geom_col(colour = "black") +
  coord_flip() +
  labs(x = " ",
       y = " ") +
  labs(title = "Organizations Receiving Most Donations Among All Owners") +
  scale_fill_brewer(palette = "Accent") +
  theme(legend.position = "bottom") +
  scale_x_discrete(labels = new_names) +
  theme(plot.title = element_text(family = "mono",
                                  face = "bold",
                                  margin = margin(c(t = 40,
                                                    b = 40)),
                                  vjust = 7,
                                  size = 18),
        axis.text = element_text(family = "mono",
                                 face = "bold"),
        axis.title = element_text(family = "mono",
                                  size = 8),
        axis.title.x = element_text(size = 10,
                                    margin = margin(t = 10,
                                                    b = 10)),
        legend.title = element_text(family = "mono",
                                    face = "bold"),
        legend.text = element_text(family = "mono",
                                   face = "bold"),
        axis.ticks = element_blank(),
        legend.key.size = unit(1, 'cm'),
         legend.box.background = element_rect()) +
    geom_text(data = recipients, aes(label = n, fontface = "bold"), size = 5, hjust = -0.25)

@@

ggplot(data = top10, aes(x = order, y = NetWorth, fill = Industry)) +
  geom_col(colour = "black") +
  coord_flip() +
  labs(x = " ", 
       y = "Net Worth",
       caption = "Measured in Billions",
       colour = "Industry",
       title = "2021 Forbes Billionaires",
       subtitle = "Examining the Billionaires with the Highest Net Worth from 2021") +
  scale_fill_viridis_d() +
  scale_x_discrete(labels = new_names2) +
  theme(legend.position = c(0.9, 0.18)) +
  theme(axis.title = element_text(family = "mono",
                                  face = "bold",
                                  margin = margin(c(t = 30,
                                                    b = 30))),
        axis.text = element_text(family = "mono"),
        axis.text.y = element_text(face = "bold"),
        axis.ticks = element_blank(),
        plot.title = element_text(family = "mono",
                                  face = "bold",
                                  margin = margin(c(t = 15,
                                                    b = 15,
                                                    vjust = 15)),
                                  size = 20),
        plot.subtitle = element_text(family = "mono",
                                     size = 12,
                                     face = "italic",
                                       vjust = 2.5),
        axis.title.x = element_text(vjust = -3,
                                    size = 15),
        axis.title.y = element_text(vjust = 2),
        legend.title = element_text(family = "mono",
                                    face = "bold",
                                    size = 15),
        legend.text = element_text(family = "mono",
                                   face = "italic",
                                   size = 10),
        plot.caption = element_text(family = "mono",
                                    face = "italic",
                                    vjust = 3,
                                    hjust = 0.5,
                                    margin = margin(c(t = 30,
                                                      b = 30)),
                                    size = 14),
        legend.key.width = unit(1, 'cm'),
        legend.key.height = unit(1, 'cm'),
  legend.box.background = element_rect())
```

@@

outliers_age <- countries_10 %>% filter(age < 25 | age > 97)
outliers_age

countries_10_no_missing_values <- countries_10 %>% filter(!is.na(age))
countries_10_no_missing_values

countries_10_average_age <- filter %>% group_by(Country) %>%
  summarise(Average = mean(age)) %>%
  arrange(desc(Average)) %>% 
  mutate(order = fct_reorder(.f = Country, .x = Average))
countries_10_average_age

countries_10_average_age %>% arrange(desc(Average))
countries_10_average_age %>% arrange(Average)

level_order3 <- factor(countries_10$Country, level = c('China',
                                                                   'Russia',
                                                                   'Brazil',
                                                                   'Germany',
                                                                   'Canada',
                                                                   'Hong Kong',
                                                                   'United States',
                                                                   'United Kingdom',
                                                                   'India',
                                                       'Italy'))

ggplot(data = countries_10, aes(x = level_order3, y = age)) +
  geom_point(alpha = 0.7, colour = "goldenrod1") +
  coord_flip() +
  geom_point(data = countries_10_average_age, aes(x = Country, y = Average, colour = "Mean Age of Billionaires"),
             size = 6,
             shape = 18) +
  scale_colour_manual(values = c("Mean Age of Billionaires" = "navy")) +
  labs(x = " ", 
       y = " ",
       title = "Average Age of Billionaires by Country") +
  theme(legend.position = "bottom") +
  theme(axis.title = element_text(family = "mono",
                                  face = "bold"),
        axis.text = element_text(family = "mono"),
        axis.text.y = element_text(face = "bold"),
        axis.text.x = element_text(face = "bold"),
        plot.title = element_text(family = "mono",
                                  face = "bold",
                                  size = 18,
                                  margin = margin(c(t = 50,
                                                    b = 50)),
                                  vjust = 10),
        axis.ticks = element_blank(),
        legend.title = element_blank(),
        legend.text = element_text(family = "mono",
                                   face = "bold"), 
        plot.caption = element_text(family = "mono",
                                    size = 9,
                                    face = "italic"),
        legend.key.size = unit(1.2, 'cm'),
  legend.box.background = element_rect())
```

## Outliers labeled 
```{r}
ggplot(data = countries_10, aes(x = Country, y = age)) +
  geom_point(alpha = 0.4, size = 1.5, colour = "goldenrod1") +
  coord_flip() +
  geom_point(data = filter2, aes(x = order, y = Average, colour = "Mean Age of Billionaires"),
             size = 2.5) +
  scale_colour_manual(values = c("Mean Age of Billionaires" = "navy")) +
  labs(x = "Country", 
       y = "Age",
       title = "Average Age of Billionaires by Country") +
  theme(legend.position = "bottom") +
  theme(axis.title = element_text(family = "mono",
                                  face = "bold"),
        axis.text = element_text(family = "mono"),
        plot.title = element_text(family = "mono",
                                  face = "bold"),
        axis.ticks = element_blank(),
        legend.title = element_blank(),
        legend.text = element_text(family = "mono",
                                   face = "italic"), 
        plot.caption = element_text(family = "mono",
                                    size = 9,
                                    face = "italic")) +
  theme(legend.position = "none") +
    geom_label_repel(data = outliers_age, aes(label = age))

  ggplot(data = countries_10, aes(x = level_order3, y = age)) +
  geom_point(alpha = 0.7, colour = "goldenrod1") +
  coord_flip() +
  geom_point(data = countries_10_average_age, aes(x = Country, y = Average, colour = "Mean Age of Billionaires"),
             size = 6,
             shape = 18) +
  scale_colour_manual(values = c("Mean Age of Billionaires" = "navy")) +
  labs(x = " ", 
       y = " ",
       title = "Average Age of Billionaires by Country") +
  theme(legend.position = "bottom") +
  theme(axis.title = element_text(family = "mono",
                                  face = "bold"),
        axis.text = element_text(family = "mono"),
        axis.text.y = element_text(face = "bold"),
        axis.text.x = element_text(face = "bold"),
        plot.title = element_text(family = "mono",
                                  face = "bold",
                                  size = 18,
                                  margin = margin(c(t = 50,
                                                    b = 50)),
                                  vjust = 10),
        axis.ticks = element_blank(),
        legend.title = element_blank(),
        legend.text = element_text(family = "mono",
                                   face = "bold"), 
        plot.caption = element_text(family = "mono",
                                    size = 9,
                                    face = "italic"),
        legend.key.size = unit(1.2, 'cm'),
  legend.box.background = element_rect()) 
```

@@

ggplot(data = above_or_below_us, aes(x = order, y = networth, colour = above_avg)) +
  geom_segment(aes(x = order, xend = order, y = avg, yend = networth)) +
  geom_point() +
  scale_colour_brewer(palette = "Accent") +
  coord_flip() +
  labs(x = " ",
      y = "Net Worth",
      caption = "Measured in Billions",
      colour = "Average",
      title = "Billionaires In The Fashion Industry",
      subtitle = "Do these billionaires fall above or below the average billionaire net worth in the U.S.?") +
  theme(axis.text = element_text(family = "mono"),
        axis.title = element_text(family = "mono"),
        legend.text = element_text(family = "mono",
                                   face = "bold"),
        legend.title = element_text(family = "mono",
                                    face = "bold",
                                    size = 10),
        plot.caption = element_text(family = "mono",
                                    hjust = 0.5,
                                    size = 15, 
                                    vjust = 1,
                                    margin = margin(c(t = 10,
                                                      b = 20))),
        plot.title = element_text(family = "mono",
                                  face = "bold",
                                  margin = margin(c(t = 20,
                                                    b = 20)),
                                  vjust = 2.5, 
                                  size = 20),
        plot.subtitle = element_text(family = "mono",
                                     face = "italic",
                                     margin = margin(c(t = 10, b = 10)),
                                     vjust = 2.5,
                                     size = 15),
        axis.title.x = element_text(face = "bold",
                                    margin = margin(c(t = 10, b = 10)),
                                    size = 15),
        axis.text.y = element_text(face = "italic",
                                   size = 10),
        axis.ticks = element_blank(),
        legend.box.background = element_rect(),
        legend.position = c(0.885, 0.2),
         legend.key.width = unit(5, 'cm'),
        legend.key.height = unit(3, 'cm'))
```

@@

ggplot(data = country_30, aes(x = order, y = n)) +
  geom_point(colour = "orange") +
  geom_segment(aes(x = order, xend = order, y = 0, yend = n), colour = "blue", linetype = "dotdash") +
  coord_flip() +
  theme_light() +
  theme(axis.ticks.x = element_blank()) +
  labs(x = " ", 
       y = " ",
       title = "How Many Billionaires Are There From the Top 30 Countries?") +
  theme(plot.title = element_text(family = "mono",
                                  size = 20,
                                  face = "bold",
                                   margin = margin(c(t = 40,
                                                    b = 50)),
                                  vjust = 5),
        axis.text = element_text(family = "mono",
                                 face = "bold"),
        axis.title = element_text(family = "mono")) +
  geom_text(aes(label = n, fontface = "bold", family = "mono"), hjust = -0.5, size = 5, colour = "black")
```

## bar plot
```{r}
ggplot(data = country_30, aes(x = order, y = n, fill = n)) +
  geom_col(colour = "black") +
  coord_flip() +
  labs(x = " ", 
       y = " ",
       title = "How Many Billionaires Are There From the Top 30 Countries?",
       fill = "Count") +
  theme(plot.title = element_text(family = "mono",
                                  face = "bold",
                                  size = 20,
                                   margin = margin(c(t = 40,
                                                    b = 50)),
                                  vjust = 5),
        axis.text = element_text(family = "mono",
                                 face = "bold"),
        axis.title = element_text(family = "mono"),
        legend.title = element_text(family = "mono"),
        legend.text = element_text(family = "mono"),
        axis.ticks = element_blank(),
        legend.position = "none") +
  scale_fill_viridis_b(n.breaks = 6) +
  geom_text(aes(label = n, fontface = "bold", family = "mono"), hjust = -0.5, size = 5, colour = "black")
```

## How many are self-made (from entire list) ? 
```{r}
forbes_billionaires %>% select(Self_made, everything())
self_made <- forbes_billionaires %>% group_by(Self_made) %>%
  summarise(n = n()) %>%
  filter(!is.na(Self_made))

ggplot(data = self_made, aes(x = Self_made, y = n, fill = Self_made)) +
  geom_col(colour = "black") +
  scale_fill_brewer(palette = "Spectral") +
  labs(x = " ",
       y = " ",
       title = "How Many of These Billionaires Are Self-Made?",
       fill = " ") +
  theme(plot.title = element_text(family = "mono",
                                  face = "bold",
                                  margin = margin(c(t = 30)),
                                  vjust = 8,
                                  size = 20),
        legend.text = element_text(family = "mono"),
        axis.text = element_text(family = "mono"),
        axis.text.x = element_text(size = 15,
                                   face = "bold"),
        axis.ticks = element_blank(),
        axis.text.y = element_blank(),
        legend.position = "none") +
  geom_label(data = self_made, aes(label = n),
              fill = "white",
             label.size = 0.5) 
```

## Continuing to mess around 
```{r}
industry <- billionaires %>% group_by(Industry) %>%
  summarise(n = n()) %>%
  arrange(desc(n))
industry

combined_billionaires <- left_join(forbes_billionaires, billionaires, by = c("Name" = "Name"))

combined_billionaires2 <- combined_billionaires %>% separate(col = Education, into = c("Degree", "University"),
                                 sep = ", ")

harvard <- combined_billionaires2 %>% filter(University == "Harvard University") 
harvard

harvard %>% group_by(Industry) %>%
  summarise(n = n()) %>%
  arrange(desc(n))

ggplot(data = harvard, aes(x = Degree, y = NetWorth.x)) +
  geom_point() +
  coord_flip()

@@

tidy_education %>% filter(University == "Harvard University")

@@

ggplot(data = tidy_education2, aes(x = Degree, y = NetWorth)) +
  geom_violin() +
  coord_flip()
```

## usa billionaires
```{r}
library(plotly)
us_forbes_billionaires <- combined_billionaires %>% filter(Country.x == "United States")
us_forbes_billionaires

us_forbes_billionaires %>% group_by(Industry) %>%
  summarise(n = n()) %>%
  arrange(desc(n))

plot10 <- ggplot(data = us_forbes_billionaires, aes(x = NetWorth.x, y = Age.x,
                                                    label = Name, colour = Industry)) +
  geom_jitter() +
  labs(x = "NetWorth",
       y = "Age",
       title = "Billionaires in the U.S.") +
  theme(plot.title = element_text(face = "bold",
                                  size = 15,
                                  margin = margin(c(t = 10, b = 10))),
        axis.ticks = element_blank(),
        legend.title = element_text(face = "bold"),
        axis.title = element_text(face = "bold"))

ggplotly(plot10, tooltip = "label")
```

## Map
```{r}
library(maps)
library(tidyverse)
state_df <- ggplot2::map_data("state")

forbes_billionaires_geo <- read_csv("data/forbes_billionaires_geo.csv")
forbes_billionaires_geo %>% select(geometry, everything())
forbes_billionaires_geo %>% separate(col = geometry, into = c(""))
```

## New Data Set
```{r}
pvp_dataset <- read_csv("data/pvp_dataset.csv")
pvp_dataset

ggplot(data = pvp_dataset, aes(x = year, y = salary)) +
  geom_line()
pvp_dataset_2 <- read_csv("data/pvp_dataset 2.csv")
pvp_dataset_2
```
